Providing better confidentiality and authentication on the Internet using Namecoin and MinimaLT

### 2014-01-09 paper.tex
Release

@@

\subsection{Another subsection will come here}

@@

\section{Confession}

This paper initially aimed at digging deeper into the crypto and protocol stuff but because of concurring deadlines, this in-depth analysis of the protocols is pushed back to another paper. :)

\section{Acknowledgments}

Still to do 
\bibliographystyle{abbrv}
\bibliography{bibliography}

>>>>

\subsection{Defining user privacy}

The solutions brought forward in this paper are attempts to fix \emph{confidentiality and authentication} on the Internet. \emph{Anonymity is not provided.} Although, an attacker could still get a significant amount of metadata because IP headers are left unchanged, MinimaLT does provide a similar traffic analysis protection as IPSec by using tunnels.

Unfortunately, because MinimaLT runs over UDP it is not possible to use it through the Tor network.\footnote{If MinimaLT proves to be a safer and faster alternative to TLS, I imagine that the Tor project would look into implementing it to speed up the network and make relay connections safer.}

@@

@@

\section{Confession}
This paper initially aimed at digging deeper into the crypto and protocol stuff but because of concurring deadlines I couldn't dig as deep in the MinimaLT protocol as I originally intended to.

\section{Acknowledgments}
I would like to thank everyone who provided feedback and reviewed this paper. Particularly, 
\begin{itemize}
\item Greg Slepak who is currently working on the DNSNMC implementation and author of the OkTurtles\cite{okTurtles} paper for providing very valuable feedback to improve this paper.
\item All folks from Noisy Square at \#30c3 for the insightful discussions that influenced this paper.
\item Dylan Bourgeois, a friend of mine, for spotting so many typos.
\end{itemize}

\section{Ressources}

The source of this paper is available on GitHub along with some of the resources used to write this paper: \newline
\url{https://github.com/FredericJacobs/safeweb}

\bibliographystyle{abbrv}
\bibliography{bibliography}
